Tropical Andes frugivore trait data Frugivoria

### 2024-06-14 code/L0/L0_TropicalAndes_frugivores_frugivoria_traits.Rmd
update file paths, add dplyr package, update summary with summary function, update output paths, add citations and package info

---
title: "Tropical Andes frugivore trait data Frugivoria"
author: "Hazel J. Anderson"
project: "Plant-Frugivore Diversity"
collaborators: "Beth E. Gerstner, Phoebe L. Zarnetske"
overview: ""
data input: ""
data output: ""
date: "2023-07-18"
output: html_document
---

# Set file paths
```{r}
data_path<-file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
output_path<- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
output_path2<- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L1')
```

@@

```{r}
print("The number of records is")
nrow(Frugivoria)
print("The number of species is" )
length(unique(Frugivoria$species))
print("The number of families is" )
length(unique(Frugivoria$family))
```

# Extract species list
```{r}
Frugivoria_SpeciesList <- unique(Frugivoria$species)
```

# Write data to csv
```{r}
TropicalAndes_Frugivoria_path <- file.path(output_path,"TropicalAndes_Frugivoria_frugivore_traits.csv") 
write.csv(Frugivoria, file = TropicalAndes_Frugivoria_path)
Frugivoria_species_path <- file.path(output_path,"TropicalAndes_Frugivoria_frugivore_traits_species.csv") 
write.csv(Frugivoria_SpeciesList, file = Frugivoria_species_path)
Frugivore_LookupTable_path <- file.path(output_path2,"TropicalAndes_frugivore_LookupTable.csv") 
write.csv(Frugivore_LookupTable, file = Frugivore_LookupTable_path)
```

>>>>

---
title: "Tropical Andes frugivore trait data Frugivoria"
author: "Hazel J. Anderson"
project: "Plant-Frugivore Diversity"
collaborators: "Beth E. Gerstner, Phoebe L. Zarnetske"
overview: "This script retrived the Frugivoria database from EDI."
#data input: "None"
#data output: "TropicalAndes_Frugivoria_frugivore_traits.csv, TropicalAndes_Frugivoria_frugivore_traits_species.csv, TropicalAndes_frugivore_LookupTable.csv"
date: "2023-07-18"
output:
  html_document:
    highlight_downlit: TRUE
    df_print: tibble
---

# Set file paths
```{r}
data_path_L0 <- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
output_path_L0 <- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
output_path_L1 <- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L1')
```

# Load required packages
```{r}
library(dplyr)
```

@@

```{r}
source("~/GitHub/neotropical_plants/code/data_summary.R")
```

```{r}
data_summary(Frugivoria, Frugivoria$IUCN_species_name, Frugivoria$genus, Frugivoria$family)
```

# Extract species list
```{r}
Frugivoria_SpeciesList <- unique(Frugivoria$IUCN_species_name)
length(Frugivoria_SpeciesList)
```

# Write data to csv
```{r}
write.csv(Frugivoria, file = file.path(output_path_L0,"TropicalAndes_Frugivoria_frugivore_traits.csv"))
write.csv(Frugivoria_SpeciesList, file = file.path(output_path_L0,"TropicalAndes_Frugivoria_frugivore_traits_species.csv"))
write.csv(Frugivore_LookupTable, file = file.path(output_path_L1,"TropicalAndes_frugivore_LookupTable.csv"))
```

# Package citations and session info
```{r}
library(report)
report::cite_packages()

devtools::session_info()
```
